Remote Collection of Respiratory Samples

### 2023-12-19 Jordana Hoppe/Home Collection/manuscript.qmd
home collection manuscript tables done

```{r data cleaning, include=FALSE}
# Use REDCap import
source("/Users/timvigers/GitHub/CF/Jordana Hoppe/Home Collection/home_collection_data.r")
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
```

# Table

```{r}
#| label: tbl-1
#| tbl-cap: Participant Characteristics
data %>%
  select(
    age, pt_sex.factor, race, ethnicity.factor, mutation1.factor,
    mutation2.factor, rural_location.factor, fev1_pp, fvc_pp
  ) %>%
  mutate(
    mutation1.factor = droplevels(mutation1.factor),
    mutation2.factor = droplevels(mutation2.factor)
  ) %>%
  tbl_summary(
    label = labels, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) 
```

# Figure

```{r}
#| label: fig-planets
#| fig-cap: Planets
```

>>>>

```{r data cleaning, include=FALSE}
# Use REDCap import
source("/Users/timvigers/GitHub/CF/Jordana Hoppe/Home Collection/home_collection_data.r")
source("/Users/timvigers/GitHub/CF/Jordana Hoppe/Home Collection/home_collection_surveys.r")
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
survey_labels <- label(survey_data)[which(label(survey_data) != "")]
survey_labels[paste0(names(survey_labels), ".factor")] <- as.character(survey_labels)
labels = c(labels,survey_labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
```

# Table 1: Participant Characteristics

```{r}
#| label: tbl-1
#| tbl-cap: Participant Characteristics
data %>%
  select(
    age, pt_sex.factor, race, ethnicity.factor, mutation1.factor,
    mutation2.factor, rural_location.factor, fev1_pp, fvc_pp
  ) %>%
  mutate(
    mutation1.factor = droplevels(mutation1.factor),
    mutation2.factor = droplevels(mutation2.factor)
  ) %>%
  tbl_summary(
    label = labels, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  as_kable_extra()
```

It appears that the two participants who were previously marked as unknown race are now considered more than one race.

# Table 2: Survey Results

```{r}
#| label: tbl-2
#| tbl-cap: Survey Results
survey_data %>%
  select(q1.factor:q6b___4.factor) %>%
  tbl_summary(
    label = labels, missing_text = "Missing"
  ) %>%
  as_kable_extra()
```

# Table 3: Clinic Culture Results

```{r}
#| label: tbl-3
#| tbl-cap: Clinic Culture Results
data %>%
  select(clinic_cx_source.factor:clinic_burk_sp.factor) %>%
  tbl_summary(
    label = labels, missing_text = "Missing"
  ) %>%
  as_kable_extra()
```

# Table 4: Research Culture Results

```{r}
#| label: tbl-4
#| tbl-cap: Research Culture Results
data %>%
  select(research_cx.factor:res_burk_sp.factor) %>%
  tbl_summary(
    label = labels, missing_text = "Missing"
  ) %>%
  as_kable_extra()
```

For Yes/No variables in @tbl-2 through @tbl-4, the percentage of "Yes" answers is shown.
